How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-22 research/paper/draft-editing.tex
expanding cosmological constraint metric discussion

The fundamental assumption underlying the concept of photo-$z$ estimation is that each galaxy $i$ has some observed photometric data $\vec{d}_{i}$ (fluxes, magnitudes, or colors) that is drawn from a function of its redshift $z_{i}$, which is a parameter in this model.  The redshifts $\{z_{i}\}$ for all galaxies in a survey are random draws from the redshift distribution, whose parameters  $\vec{\phi}$ under a chosen functional form are called \textit{hyperparameters} because they are shared among all $N$ galaxies in the survey.  Fig. \ref{fig:pgm} illustrates these relationships.  PGMs of this structure are \textit{hierarchical} in that, though the data are only directly influenced by their redshift parameters, we can still use them to infer something about the global hyperparameters by way of a higher level in the graph.

@@

The DAG of Fig. \ref{fig:pgm} translates directly into a mathematical expression for the posterior distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of the hyperparameters given the entire dataset given the set of interim posteriors $\{p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*})\}$ by way of the following derivation.  From this point forward, we will use log probabilities.

According to Bayes' rule, the posterior distribution of interest is
\begin{align}
\log p(\vec{\phi} | \{\vec{d}_{i}\}) &\propto \log p(\{\vec{d}_{i}\} | \vec{\phi}) + \log p(\vec{\phi}),
\end{align}
where $p(\vec{\phi})$ is the textit{hyperprior} probability distribution over possible values of the hyperparameters.  The hyperprior is a choice made by those performing the inference and is not to be confused with the interim prior parameters that influence the photo-$z$ PDF data product.

Focusing on the likelihood term $p(\{\vec{d}_{i}\} | \vec{\phi})$, we employ the power of the hierarchical model through \textit{marginalization} of the unobserved redshift parameters by integrating over them to obtain 
\begin{align}
% \log p(\{\vec{d}_{i}\} | \vec{\phi}) &= \log\[\int\ \exp\[\log\[p(\{\vec{d}_{i}\} | \{z_{i}\})\] + \log\[p(\{z_{i}\} | \vec{\phi})\]\]\ d\{z_{i}\}\].
\end{align}

@@

Because the mock data is associated with true values of the cosmological parameters, we may compare the quality of cosmological constraints.

\textbf{Check Dark Energy Task Force metrics on error ellipses, multi-dimensional KLD, centroid offset, etc.}

>>>>

The fundamental assumption underlying the concept of photo-$z$ estimation is that each galaxy $i$ has some observed photometric data $\vec{d}_{i}$ (fluxes, magnitudes, or colors) that is drawn from a function of its redshift $z_{i}$, which is a parameter in this model.  This function constitutes a forward model for the observations.  The redshifts $\{z_{i}\}$ for all galaxies in a survey are random draws from the redshift distribution, whose parameters  $\vec{\phi}$ under a chosen functional form are called \textit{hyperparameters} because they are shared among all $N$ galaxies in the survey.  Fig. \ref{fig:pgm} illustrates these relationships.  PGMs of this structure are \textit{hierarchical} in that, though the data are only directly influenced by their redshift parameters, we can still use them to infer something about the global hyperparameters by way of a higher level in the graph.

@@

The DAG of Fig. \ref{fig:pgm} translates directly into a mathematical expression for the posterior distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of the hyperparameters given the entire set of interim posteriors $\{p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*})\}$ by way of the following derivation.  From this point forward, we will use log probabilities.

According to Bayes' rule, the posterior distribution of interest is
\begin{align}
\log p(\vec{\phi} | \{\vec{d}_{i}\}) &\propto \log p(\{\vec{d}_{i}\} | \vec{\phi}) + \log p(\vec{\phi}),
\end{align}
where $p(\vec{\phi})$ is the \textit{hyperprior} probability distribution over possible values of the hyperparameters.  The hyperprior is a choice made by those performing the inference and is not to be confused with the interim prior parameters that influence the photo-$z$ PDF data product.

Focusing on the likelihood term $p(\{\vec{d}_{i}\} | \vec{\phi})$, we employ the power of the hierarchical model through \textit{marginalization} of the unobserved redshift parameters by integrating over them to obtain 
\begin{align}
\log[p(\{\vec{d}_{i}\} | \vec{\phi})] &= \log[\int\exp[\log[p(\{\vec{d}_{i}\} | \{z_{i}\})]\\
& + \log[p(\{z_{i}\} | \vec{\phi})]]\ d\{z_{i}\}].
\end{align}

@@

Because the realistic mock data of Sec. \ref{sec:buzzard} is associated with true values of the cosmological parameters, we may compare the quality of cosmological constraints under different estimators of $n(z)$, creating a figure like Fig. \ref{eq:scgsr}.  We perform this analysis using a forecasting code that takes $n(z)$ and produces projected error ellipses in the space of cosmological parameters.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{cosmo_constraints.png}
		\caption{[I'd like to be able to make a plot like this with the different $n(z)$ estimators produced by \texttt{chippr} from the same set of photo-$z$ PDFs.  Then I can calculate some metrics of the accuracy and precision of the error distributions relative to the true values of the cosmological parameters that produced the mock data.]}
		\label{fig:scgsr}
	\end{center}
\end{figure}

% \textbf{Check Dark Energy Task Force metrics on error ellipses, multi-dimensional KLD, centroid offset, etc.}

### 2017-06-22 research/paper/draft.tex
expanding cosmological constraint metric discussion

The DAG of Fig. \ref{fig:pgm} translates directly into a mathematical 
expression for the posterior distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of 
the hyperparameters given the entire dataset given the set of interim 
posteriors $\{p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*})\}$ by way of the following 
derivation.  From this point forward, we will use log probabilities.

According to Bayes' rule, the posterior distribution of interest is
\begin{align}
\log p(\vec{\phi} | \{\vec{d}_{i}\}) &\propto \log p(\{\vec{d}_{i}\} | 
\vec{\phi}) + \log p(\vec{\phi}),
\end{align}
where $p(\vec{\phi})$ is the textit{hyperprior} probability distribution over 
possible values of the hyperparameters.  The hyperprior is a choice made by 
those performing the inference and is not to be confused with the interim prior 
parameters that influence the photo-$z$ PDF data product.

Focusing on the likelihood term $p(\{\vec{d}_{i}\} | \vec{\phi})$, we employ 
the power of the hierarchical model through \textit{marginalization} of the 
unobserved redshift parameters by integrating over them to obtain 
\begin{align}
\end{align}

@@

Because the mock data is associated with true values of the cosmological 
parameters, we may compare the quality of cosmological constraints.

\textbf{Check Dark Energy Task Force metrics on error ellipses, 
multi-dimensional KLD, centroid offset, etc.}

>>>>

The DAG of Fig. \ref{fig:pgm} translates directly into a mathematical 
expression for the posterior distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of 
the hyperparameters given the entire set of interim posteriors $\{p(z_{i} | 
\vec{d}_{i}, \vec{\phi}^{*})\}$ by way of the following derivation.  From this 
point forward, we will use log probabilities.

According to Bayes' rule, the posterior distribution of interest is
\begin{align}
\log p(\vec{\phi} | \{\vec{d}_{i}\}) &\propto \log p(\{\vec{d}_{i}\} | 
\vec{\phi}) + \log p(\vec{\phi}),
\end{align}
where $p(\vec{\phi})$ is the \textit{hyperprior} probability distribution over 
possible values of the hyperparameters.  The hyperprior is a choice made by 
those performing the inference and is not to be confused with the interim prior 
parameters that influence the photo-$z$ PDF data product.

Focusing on the likelihood term $p(\{\vec{d}_{i}\} | \vec{\phi})$, we employ 
the power of the hierarchical model through \textit{marginalization} of the 
unobserved redshift parameters by integrating over them to obtain 
\begin{align}
\log[p(\{\vec{d}_{i}\} | \vec{\phi})] &= \log[\int\exp[\log[p(\{\vec{d}_{i}\} | 
\{z_{i}\})]\\
& + \log[p(\{z_{i}\} | \vec{\phi})]]\ d\{z_{i}\}].
\end{align}

@@

Because the realistic mock data of Sec. \ref{sec:buzzard} is associated with 
true values of the cosmological parameters, we may compare the quality of 
cosmological constraints under different estimators of $n(z)$, creating a 
figure like Fig. \ref{eq:scgsr}.  We perform this analysis using a forecasting 
code that takes $n(z)$ and produces projected error ellipses in the space of 
cosmological parameters.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{cosmo_constraints.png}
		\caption{[I'd like to be able to make a plot like this with the 
different $n(z)$ estimators produced by \texttt{chippr} from the same set of 
photo-$z$ PDFs.  Then I can calculate some metrics of the accuracy and 
precision of the error distributions relative to the true values of the 
cosmological parameters that produced the mock data.]}
		\label{fig:scgsr}
	\end{center}
\end{figure}
